---
title: "Project"
author: "Haiyue Wang"
output:
  pdf_document: default
  bookdown::pdf_document2:
    latex_engine: lualatex
  tufte::tufte_handout:
    latex_engine: xelatex
  html_notebook: default
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(gRain)
library(pcalg)
library(bnlearn)

#install.packages("vioplot")
library(vioplot)
```

# Data Preprocessing

## Read data

```{r message=FALSE, warning=FALSE}
data <- read_csv(
  "https://seamice.github.io/data/unisa/DataProfessionDev/data/melb_house_withnum.csv", 
  col_names = TRUE
)
#data.no.class <- data %>% select(-class)

data
```

```{r}
names(data)

data_without_region <- data %>% select(
  -SUBURB, -ADDRESS, -SELLERG, -DATE, 
  -POSTCODE, -COUNCILARE, -REGIONNAME
)
data_without_region
```

## Task 1: Dealing with Missing values

```{r}
b <- summary(data_without_region %>% select(CAR, BUILDINGAR, YEARBUILT, AREANUM))
#as.data.frame(b)
b
```

```{r message=FALSE, warning=FALSE}
#install.packages("mice")
library(mice)
```

```{r}
data.imputed <- mice(
  #data_without_region %>% select(-PRICE), 
  data_without_region %>% select(CAR, BUILDINGAR, YEARBUILT, AREANUM),
  m=3, 
  maxit = 50, 
  method = 'pmm', 
  seed = 500)
#summary(data.imputed)
```

```{r}
data.complete <- complete(data.imputed, 2)
summary(data.complete)
```

```{r}
data.no.missing <- cbind(
  data_without_region %>% select(-CAR, -BUILDINGAR, -YEARBUILT, -AREANUM), 
  data.complete
)
data.no.missing
```

## Task 2: Make levels for price

```{r}
data$city="Melbourne"
ggplot(data, aes(x = city, y = PRICE)) +
  geom_violin() + 
  stat_summary(fun = function(x){
                   mean(x) + (mean(x)-min(x))
               },
               geom = "crossbar", 
               width = 0.5,
               colour = "red")
#data.no.missing <- data.no.missing %>% select(-city)
```

According to the prices, we make the price greater than [4e06, infinate) is high price group, between [3e06, 4e06) is middle price group, all others belongs to low normal price group.

```{r}
#data.no.missing %>%
#  mutate(a = )
#d <- lapply(data.no.missing$PRICE, function (x) ifelse(x < 3e06, 'N', ifelse(x < 4e06, 'M', 'H')))
#d <- lapply(data.no.missing$PRICE, function (x) ifelse(x < 3e06, 1, ifelse(x < 4e06, 2, 3)))

#mid <- max(data.no.missing$PRICE)/2 + min(data.no.missing$PRICE)/2
mid <- mean(data.no.missing$PRICE)
mid <- mid + (mid-min(data.no.missing$PRICE))

d <- lapply(data.no.missing$PRICE, function(x) ifelse(x<mid, 0, 1))

data.no.missing$PRICE_LEVEL<-unlist(d)

data.no.missing.pl <- data.no.missing %>% select(-PRICE)
```

## Task 3: Convert String -\> Numeric

```{r}

a<-data.frame(ch_val=unique(data.no.missing.pl$TYPE),
              new_val=1:3)
```

```{r}
unique_values <- unique(data.no.missing.pl$TYPE)
data.no.missing.pl$TYPE <- unlist(
  lapply(data.no.missing.pl$TYPE, function(x) which(unique_values == x))
)
```

```{r}
unique(data.no.missing.pl$METHOD)


a<-data.frame(ch_val=unique(data.no.missing.pl$METHOD),
              new_val=1:5)
```

```{r}
unique_values <- unique(data.no.missing.pl$METHOD)
data.no.missing.pl$METHOD <- unlist(
  lapply(data.no.missing.pl$METHOD, function(x) which(unique_values == x))
)
```

```{r}
data.no.missing.pl$PROPERTYCO <- as.numeric(
  substr(data.no.missing$PROPERTYCO,
         1,
         nchar(data.no.missing$PROPERTYCO)-1
  )
)
```

# Bayesian Network

## Task 4: Learn the global structure (CPDAG)

### `Structure learning:`pc algorithm

```{r}
library(DT)
NAMES=colnames(data.no.missing.pl)
NumNameMap <- data.frame(NUM=1:length(NAMES), NAME=NAMES)
datatable(NumNameMap)
```

```{r warning=FALSE}
pc.fit <- pc(
  suffStat = list(C = cor(data.no.missing.pl), n = nrow(data.no.missing.pl)), 
  indepTest = gaussCItest, 
  alpha=0.01, 
  #labels = colnames(data.no.missing.pl)
  labels = as.character(1:length(NAMES))  #label node names
)

#data.frame(NUM=1:50, NAME=colnames(data.no.class))
plot(pc.fit, main = "CPDAG")
```

## Task 5: Causal Effects (IDA)

### Causal Effects on PRICE_LEVEL from Other Variables

```{r warning=FALSE}
# Get gene EBF1 index
PRICE_idx <- match("PRICE_LEVEL", names(data.no.missing.pl))
CausalOnPRICE <- data.frame(
  causality = unlist(
    lapply(
      (1:length(names(data.no.missing.pl)))[-PRICE_idx], 
      function(idx){
        min(
          abs(
            idaFast(
              idx,
              PRICE_idx,
              cov(data.no.missing.pl),
              pc.fit@graph)
          )
        )
      }
    )
  ),
  variable  = names(data.no.missing.pl)[-PRICE_idx]
) 
CausalOnPRICE %>% 
  arrange(across(causality, desc))
```

## Task 6: PC-Simple

### 6.1 Find the parents and children

```{r warning=FALSE}
class.pc <- pcSelect(
  data.no.missing.pl %>% select(PRICE_LEVEL),
  data.no.missing.pl %>% select(-PRICE_LEVEL),
  alpha = 0.01
)
class.pc <- data.frame(ispc = class.pc$G, zmin = class.pc$zMin)
class.pc[order(class.pc$zmin, decreasing=TRUE),]
```

```{r warning=FALSE}
rownames(class.pc[class.pc$ispc == TRUE,])
```

### 6.2 Naïve Bayes classification

The Naive Bayes classifier is using `caret` package to train model.

```{r message=FALSE, warning=FALSE}
library(caret)
```

#### 6.2.1 Naive Bayes classification with all features

The code below using all features as input features for training.

```{r warning=FALSE}
set.seed(100)
trctrl <- trainControl(method = "cv", number = 10, savePredictions=TRUE)
ma <- train(
  factor(PRICE_LEVEL) ~., 
  data = data.no.missing.pl, 
  method = "naive_bayes", 
  trControl=trctrl, 
  tuneLength = 0
)
ma
```

#### 6.2.2 Naive Bayes classification with PC set

The code below using parents and children features of `class` feature as input features for training.

```{r warning=FALSE}
data.related <- data.no.missing.pl[,append(rownames(class.pc[class.pc$ispc == TRUE,]), "PRICE_LEVEL")]

mr <- train(
  factor(PRICE_LEVEL) ~., 
  data = data.related, 
  method = "naive_bayes", 
  trControl=trctrl, 
  tuneLength = 0
)
mr
```

# Classification Modeling

## Feature Selection

```{r warning=FALSE}
library(FSelectorRcpp)
library(ggcorrplot)
```

```{r warning=FALSE}
data.importance <- information_gain(PRICE_LEVEL ~ ., data.no.missing.pl)
data.importance <- data.importance %>% arrange(importance)
data.importance <- data.importance %>% mutate(attributes = factor(attributes, levels=attributes))

data.importance %>% 
  ggplot(aes(x=attributes, y=importance)) + 
  geom_bar(stat = "identity", fill = "darksalmon") + 
  ggtitle("Importance with PRICE_LEVEL") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Variables") +
  xlab("Importance") + 
  coord_flip()
```

```{r}
#rm.fs <- data.importance[data.importance$importance < 0.000001,]$attributes
rm.fs <- data.importance[data.importance$importance < 0.01,]$attributes
spearman <- cor(data.no.missing.pl %>% select(-rm.fs), method = "spearman")

ggcorrplot(spearman,
  hc.order = TRUE,
  type = "lower",
  colors = c("#6D9EC1", "white", "#E46726"),
  lab = TRUE
) + labs(title = "Pearson Correlation among Variables")+ theme(plot.title = element_text(hjust = 0.5))
```

```{r}
model.data <- data.no.missing.pl %>% select(-rm.fs) %>%select(-BEDROOM2)
```

## Common Functions

```{r}
get_indicator <- function(predict_ret, real_ret){
  if (class(factor(1,2,3)) != class(predict_ret))
    predict_ret = as.factor(predict_ret)
  if (class(factor(1,2,3)) != class(real_ret))
    real_ret = as.factor(real_ret)
  cm <- confusionMatrix(as.factor(predict_ret), as.factor(real_ret))
  df <- as.data.frame.matrix(cm$table)

  TP <- df['H', 'H']
  TN <- df['L', 'L']
  FN <- df['H', 'L']
  FP <- df['L', 'H']

  Accuracy <- (TP + TN)/(TP+TN+FP+FN)
  BCR <- (TP/(TP+FN) + TN/(TN+FP))/2
  Precision = TP/(TP+FP)
  Recall <- TP/(TP+FN)
  F.score <- (2*TP)/(2*TP+FP+FN)
  Kappa <- cm$overall["Kappa"]

  return (data.frame(
    'Accuracy' = Accuracy,
    'BCR' = BCR,
    'Precision' = Precision,
    'Recall' = Recall,
    'F.score' = F.score,
    'Kappa' = Kappa
  ))
}

get_test_ret <- function(model, test_data){
  input_variables <- test_data %>% select(-PRICE_LEVEL)
  test.predict <- predict(model, input_variables, type="class")
  return (get_indicator(test.predict, test_data$PRICE_LEVEL))
}

merge_indicator = function(x,y){
  if (is.null(x[[2]])){
    return (list(x[[1]], get_test_ret(y, x[[1]])))
  }
  ret <- rbind(x[[2]], (get_test_ret(y, x[[1]])))
  return (list(x[[1]], ret))
}

get_models_indicators <- function(test_data, models){
  ret = (Reduce(merge_indicator, models, list(test_data, NULL))[[2]])
  rownames(ret) <- 1:nrow(ret)
  return (ret)
}
```

## Decision Tree

```{r}
library(rpart)
```

```{r}
set.seed(1092)

model.data$PRICE_LEVEL <- unlist(
  lapply(model.data$PRICE_LEVEL, function(x) ifelse(x == 1, 'H', 'L')))

train_index <- sample(1:nrow(model.data), 0.8*nrow(model.data))
dt.train_data <- model.data[train_index,]
dt.test_data <- model.data[-train_index,]
```

```{r}
# Define the grid of parameters
dt.param_grid <- expand.grid(
  maxdepth = seq(3, 30, by=3),
  minsplit = seq(5, 50, by=5),
  minbucket = seq(5, 50, by=5)
)

# Train models with different parameters
dt.models <- lapply(1:nrow(dt.param_grid), function(i) {
  param <- dt.param_grid[i,]
  model <- rpart(
    PRICE_LEVEL ~ .,
    data = dt.train_data,
    control = rpart.control(
      maxdepth = param$maxdepth,
      minsplit = param$minsplit,
      minbucket = param$minbucket
    )
  )
  return(model)
})
```

```{r}
# indicator on training data
dt.train_data.indicator <- get_models_indicators(dt.train_data, dt.models)
dt.test_data.indicator <- get_models_indicators(dt.test_data, dt.models)

dt.param_grid$test_accuracy <- dt.test_data.indicator$Accuracy
dt.param_grid$train_accuracy <- dt.train_data.indicator$Accuracy

dt.param_grid$test_BCR <- dt.test_data.indicator$BCR
dt.param_grid$train_BCR <- dt.train_data.indicator$BCR

dt.param_grid$test_Precision <- dt.test_data.indicator$Precision
dt.param_grid$train_Precision <- dt.train_data.indicator$Precision

dt.param_grid$test_Recall <- dt.test_data.indicator$Recall
dt.param_grid$train_Recall <- dt.train_data.indicator$Recall

dt.param_grid$test_F.score <- dt.test_data.indicator$F.score
dt.param_grid$train_F.score <- dt.train_data.indicator$F.score

dt.param_grid$test_Kappa <- dt.test_data.indicator$Kappa
dt.param_grid$train_Kappa <- dt.train_data.indicator$Kappa
```

```{r}
#install.packages('plotly')
library(plotly)
```

```{r}
# Create the plot
p <- plot_ly(
  dt.param_grid, x = ~maxdepth, y = ~minsplit, z = ~minbucket,
  color = ~train_accuracy
) %>%
  add_markers() %>%
  layout(
    scene = list(xaxis = list(title = 'Max Depth'),
                 yaxis = list(title = 'Min Split'),
                 zaxis = list(title = 'Min Bucket'))
  )
t1 <- list(
  family = "Times New Roman",
  color = "red"
)
p %>% layout(title= list(text = "Train Accuracy",font = t1))
```

## Neural Networks

```{r}
#install.packages(c('neuralnet','keras','tensorflow'),dependencies = T)
library(neuralnet)
```

```{r}
train_index <- sample(1:nrow(model.data), 0.8*nrow(model.data))
neu_train_data <- model.data[train_index,]
neu_test_data <- model.data[-train_index,]
head(neu_train_data)
```

```{r}
model = neuralnet(
    PRICE_LEVEL~.,
    data=neu_train_data,
    hidden=c(13, 8, 5, 3, 2),
    linear.output = T,
)

plot(model, rep = "best")
```

```{r}
#Model Evaluation
pred <- predict(model, neu_test_data)
#test_data$target %>% unique()
labels <- c("disease", "no disease")
prediction_label <- data.frame(max.col(pred)) %>%
  mutate(pred=labels[max.col.pred.]) %>%
  select(2)

# Get indicator for test data
get_indicator(as.factor(prediction_label$pred), neu_test_data$target)
```

```{r}
# Get indicator for train data
pred <- predict(model, neu_train_data)
labels <- c("disease", "no disease")
prediction_label <- data.frame(max.col(pred)) %>%
  mutate(pred=labels[max.col.pred.]) %>%
  select(2)
get_indicator(as.factor(prediction_label$pred), neu_train_data$target)
```

## K-Nearest Neighbors.

```{r}
knn.train_index <- sample(1:nrow(model.data), 0.8*nrow(model.data))
knn.train_data <- model.data[knn.train_index,]
knn.test_data <- model.data[-knn.train_index,]
head(knn.train_data)
```

```{r}
# Define the training control
ctrl <- trainControl(method = "repeatedcv", number = 5)  # 5-fold cross-validation

# Define the parameter grid
param_grid <- expand.grid(k = 1:40)  # Vary the k parameter

# Perform grid search
knn.model <- train(
  knn.train_data %>% select(-PRICE_LEVEL),
  knn.train_data$PRICE_LEVEL,
  method = "knn",
  trControl = ctrl,
  tuneGrid = param_grid
)
```

```{r}
# The indicator on test data
get_indicator(predict(knn.model, knn.test_data), knn.test_data$PRICE_LEVEL)
```

```{r}
get_indicator(predict(knn.model, knn.train_data), knn.train_data$PRICE_LEVEL)
```

```{r}
knn.model$results %>%
  ggplot(aes(x=k,y=Accuracy)) +
  geom_point() +
  geom_line() +
  xlab('K') +
  ylab('Accuracy')+
  ylim(0.0,1) +
  ggtitle('The relationship among Train Accuracy with K ') +
  theme(plot.title = element_text(hjust = 0.5))
```
